Country-Level Impact of Education on Entrepreneurship

### 2014-11-29 FromEducationToEntrepreneurship.Rmd

To what extent do the behavioral characteristics of education systems - individualistic, group-oriented, reinforcing self-confidence - affect the rate of entrepreneurship in OECD countries?

>>>>

To what extent do the behavioural characteristics of education systems - individualistic, group-oriented, reinforcing self-confidence - affect the rate of entrepreneurship across OECD countries?
